---
title: "Vignette of the R package `micropem`"
author: "Maëlle Salmon and other CHAI project members"
date: "`r Sys.Date()`"
output:
  md_document:
    toc: true
    variant: markdown_github
---

rtimicropem
============

[![Build Status](https://travis-ci.org/ropensci/rtimicropem.svg?branch=master)](https://travis-ci.org/ropensci/rtimicropem)
[![Build status](https://ci.appveyor.com/api/projects/status/m77xbrmdktarl1e6?svg=true)](https://ci.appveyor.com/project/ropensci/rtimicropem)
[![codecov.io](https://codecov.io/github/ropensci/rtimicropem/coverage.svg?branch=master)](https://codecov.io/github/ropensci/rtimicropem?branch=master)
[![](https://badges.ropensci.org/126_status.svg)](https://github.com/ropensci/onboarding/issues/126)
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.831438.svg)](https://doi.org/10.5281/zenodo.831438)

Please note that this project is released with a [Contributor Code of Conduct](https://github.com/masalmon/rtimicropem/blob/master/CONDUCT.md). By participating in this project you agree to abide by its terms.

```{r, echo = FALSE}
knitr::opts_chunk$set(
  fig.path = "README/README-fig-"
)
```
# Installation

```{r, eval=FALSE}
library("devtools")
install_github("masalmon/rtimicropem", build_vignettes=TRUE)
```

# Introduction

```{r, echo = FALSE, warning=FALSE, message=FALSE}
library("knitr")
library("dplyr")
```

This package aims at supporting the analysis of PM2.5 measures made with RTI MicroPEM. [RTI MicroPEM](https://www.rti.org/sites/default/files/brochures/rti_micropem.pdf) are personal monitoring devices (PM2.5 and PM10) developped by [RTI international](https://www.rti.org/).

The goal of the package functions is to help in two main tasks:

* Checking individual MicroPEM output files after, say, one day of data collection.

* Building a data base based on output files, and clean and transform the data for further analysis.

For more information check out the [package website](http://www.masalmon.eu/rtimicropem), in particular the [introductory vignette](http://www.masalmon.eu/rtimicropem/articles/vignette_ammon.html).
